A comparison of design-based and model-based approaches for spatial data.

### 2021-10-04 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
updated figure and added plot notes.

@@

ggplot(data = combo_data, aes(x = n, y = rel_efficiency, colour = approach)) +
  facet_grid(psill ~ resptype) +
  geom_jitter(width = 7) +
  scale_colour_manual(values = c("goldenrod1", "goldenrod4", "mediumpurple1", "mediumpurple4"))
```

@@

ggplot(data = combo_data_grts_model, aes(x = n, y = rel_efficiency)) +
  facet_grid(psill ~ resptype) +
  geom_point()
```

@@

>>>>

Plot Note: change to 3 x 3, add third column, investigate colour vs. size.

@@

ggplot(data = combo_data, aes(x = factor(n), y = rel_efficiency, colour = approach)) +
  facet_grid(psill ~ resptype) +
  geom_jitter(width = 7) +
  scale_colour_manual(values = c("goldenrod1", "goldenrod4", "mediumpurple1", "mediumpurple4"))
```

Plot Note: change colours and think about shape
change partial sill variance to proportion of partial sill
think about legend going on graph

Plot Note: Think about raw data.

@@

ggplot(data = combo_data_grts_model, aes(x = n, y = releffgrts)) +
  facet_grid(psill ~ resptype) +
  geom_point()
```

Plot Note: Do we want this figure?

@@

Plot Note: Change to coverage plot to include all types
